Whats reported in the news?

### 2018-03-05 paper/docs/04_Modelresults_35.Rmd
add poll data

```{r eval=FALSE, fig.height=12, fig.width=5, include=FALSE}
topic <- 45

@@

```{r}
topics <- matrix(c(1, "SPD, M.Schulz", 2, "A.Merkel vs. Schulz", 3, "Jamaica coalition", 4, "Diesel scandal", 5, "H.Kohl", 6, "Federal Elections", 7, "EU policies, refugees", 8, "Political trends in GER", 9, "AfD in Parliament", 10, "A.Merkel", 11, "Hamburg G20", 12, "Christian, Berlin, Bruch", 13, "Climate policy, Die Grünen", 14, "Seehofer vs. Söder", 15, "D.Trump", 16, "Great coalition", 17, "CDU/CSU", 18, "Elections in Niedersachen", 19, "Budget statistics, Welfare policy", 20, "AfD in social media", 21, "DIE LINKE", 22, "German armed forces, Mali", 23, "Weather, Bahn", 24, "Innenministerium, Verfassungsschutz", 25, "Terror attack (Amri)", 26, "G20 in Hamburg", 27, "Spahn (CDU)", 28, "Steinmeier", 29, "German armed forces", 30, "AfD", 31, "Women empowerment", 32, "Diplomatic relations w Turkey, Russia", 33, "Election polls", 34, "Votings in parliament", 35, "F.Petri, Staatsanwaldschaft"), ncol=2, byrow=T)

@@

```{r}
keep <- c(1,2,6,8,14,16,17,18,24,29,31,35,38,40,41,43)
```

@@

@@

```{r, message=FALSE, warning=FALSE, include=FALSE}
df <- btw.2 %>%
  filter(gamma >= 0.75) %>%
  filter(topic %in% keep)

@@

#### 1. by topic
```{r fig.height=8, fig.width=6}

p <- sentDF.values %>%
  group_by(topic_name) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n())

ggplot(p, aes(reorder(topic_name, sentiment), 
              sentiment)) +
  geom_col(aes(fill=p$obs)) +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  labs(x="", y="",
       title = "Grouped Sentiment value",
       fill = "Number of\nObservations") +
  theme(axis.text.y = element_text(size = 10))
```

@@

ggplot(p, aes(reorder(site, sentiment), 
              sentiment)) +
  geom_col(aes(fill=p$obs)) +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  labs(x="", y="",
       title = "Grouped Sentiment value",
       fill = "Number of\nObservations") +
  theme(axis.text.y = element_text(size = 10))
```

@@

ggplot(p, 
       aes(reorder(topic_name, topic), 
           sentiment)) +
  geom_col(aes(fill=p$obs)) +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  facet_wrap(~site, ncol = 7) +
  labs(x="", y="", fill= "Number of\nObservations",
       title = "Sentiment value") +
  theme(axis.text.y = element_text(size=12))
```

@@

<img src="../figs/radarchart_Bild.de45.png", width = "45%">
<img src="../figs/radarchart_DIE WELT45.png", width = "45%">
<img src="../figs/radarchart_FOCUS ONLINE45.png", width = "45%">
<img src="../figs/radarchart_SPIEGEL ONLINE45.png", width = "45%">
<img src="../figs/radarchart_stern.de45.png", width = "45%">
<img src="../figs/radarchart_Tagesschau.de45.png", width = "45%">
<img src="../figs/radarchart_ZEIT ONLINE45.png", width = "45%">

>>>>

```{r eval=FALSE, fig.height=12, fig.width=5, include=FALSE}
topic <- 35

@@

```{r}
topics <- matrix(c(1, "SPD, M.Schulz", 2, "A.Merkel vs. Schulz", 3, "Jamaica coalition", 4, "Diesel scandal", 5, "H.Kohl", 6, "A.Merkel", 7, "Federal Election Results", 8, "Seehover vs. Söder, CSU", 9, "EU policies, refugee policy", 10, "German Parliament, parliamentarians", 11, "Mix: DIE LINKE, W.Schäuble", 12, "Refugees, deportation", 13, "Mix: Schröder, IT Topics", 14, "B90/Die Grünen", 15, "USA, Russia, Israel", 16, "Great coalition", 17, "A.Weidel (AfD)", 18, "Budget statistics, Welfare policy", 19, "Process Error", 20, "Federal Constitutional Court, Ministry of the Interior", 21, "German armed forces, Mali", 22, "Mix: Weather, DB, nuclear transport, ...", 23, "Elections in Niedersachsen", 24, "CDU / CSU", 25, "Mix: political talkshows, Berxit, Macron", 26, "Mix: F.-W.Steinmeier, Constitution, H.Maas", 27, "public statistics", 28, "Election polls", 29, "F.Petry, Gauland (AfD)", 30, "Mix: NSU, sexism", 31, "German armed forces, V.d.Leyen", 32, "G20 in Hamburg", 33, "Turkey, S.Gabriel", 34, "police reports, terror (left-, right-wing, IS)", 35, "Seehofer, refugee cap"), ncol=2, byrow=T)

@@

```{r}
keep <- seq(1:k)
```

@@

```{r}
keep <- c(1,16,24,29,3,6,8)
```

@@

```{r, message=FALSE, warning=FALSE, include=FALSE}
df <- btw.2 %>%
  filter(gamma >= 0.8) %>%
  filter(topic %in% keep)

@@

#### 1. by topic
```{r fig.height=8, fig.width=6}
p <- sentDF.values %>%
  group_by(topic_name) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n())

ggplot(p, aes(reorder(topic_name, sentiment), 
              sentiment,
              label = obs)) +
  geom_col(fill = col[1], alpha = 0.7) +
  geom_text() +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  labs(x="", y="",
       title = "Grouped Sentiment value",
       fill = "Number of\nObservations") +
  theme(axis.text.y = element_text(size = 10))
```

@@

ggplot(p, aes(reorder(site, sentiment), 
              sentiment,
              label = obs)) +
  geom_col(fill = col[3], alpha = 0.7) +
  geom_text() +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  labs(x="", y="",
       title = "Grouped Sentiment value",
       fill = "Number of\nObservations") +
  theme(axis.text.y = element_text(size = 10))
```

@@

ggplot(p, 
       aes(reorder(topic_name, topic), 
           sentiment, label = obs)) +
  geom_col(fill=col[1], alpha = 0.7) +
  geom_text() +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  facet_wrap(~site, ncol = 7) +
  labs(x="", y="", fill= "Number of\nObservations",
       title = "Sentiment value") +
  theme(axis.text.y = element_text(size=12))
```

```{r}
sentDF.values %>%
  filter(topic == 6) %>%
  select(title, sentiment, site) %>%
  htmlTable::htmlTable(align = "l")
```

@@

<img src="../figs/radarchart_Bild.de35.png", width = "49%">
<img src="../figs/radarchart_DIE WELT35.png", width = "49%">
<img src="../figs/radarchart_FOCUS ONLINE35.png", width = "49%">
<img src="../figs/radarchart_SPIEGEL ONLINE35.png", width = "49%">
<img src="../figs/radarchart_stern.de35.png", width = "49%">
<img src="../figs/radarchart_Tagesschau.de35.png", width = "49%">
<img src="../figs/radarchart_ZEIT ONLINE35.png", width = "49%">

### Compare with polls
```{r eval=FALSE, include=FALSE}
load("../output/polls.Rda")
```

Define Functions

```{r eval=FALSE, include=FALSE}
calculate_month = function(month, year) {
  date <- ymd(paste(year, 1, 1, sep="-"))
  month(date) = month
  return(date)
}

normalize_data <- function(x) {
  y <- (x - min(x, na.rm = T)) / (max(x, na.rm = T) - min(x, na.rm = T))
  return(y)
}
```

Prepare Dataframes

```{r eval=FALSE, include=FALSE}
polls <- table_long %>%
  mutate(month=month(Datum),
         year = year(Datum),
         yearmonth = calculate_month(month,year),
         val_norm = normalize_data(value)) %>%
  group_by(yearmonth,party) %>%
  summarise(mean_val = mean(value, na.rm=T),
            mean_val_norm = mean(val_norm)) %>%
  ungroup() %>%
  filter(mean_val != "NaN") %>%
  select(party, yearmonth, mean_val_norm) %>%
  spread(party, mean_val_norm)
```

```{r eval=FALSE, include=FALSE}
sentDF.values %>%
  mutate(year = year(date),
         month = month(date),
         yearmonth = calculate_month(month,year),
         sentiment_norm = normalize_data(sentiment)) %>%
  group_by(yearmonth, topic_name, topic, site) %>%
  summarise(mean_sent = mean(sentiment, na.rm=T),
            mean_sent_norm = mean(sentiment_norm, na.rm = T)) %>%
  ungroup() %>%
  left_join(polls, by="yearmonth") -> p
```

Plot

```{r eval=FALSE, include=FALSE}
for (i in unique(p$site)) {

  p1 <- p %>%
  filter(site == i) %>%
  ggplot(aes(yearmonth, mean_sent_norm,
               group = site)) +
  geom_point(show.legend = F, color = col[1]) + 
  geom_line(color = col[1]) +

  scale_y_continuous(limits = c(0,1)) +
  scale_x_date(breaks = date_breaks("1 month"), 
               labels = date_format("%b", tz = "CET")) +
  # AfD
  geom_point(aes(yearmonth, AfD), size= 0.5,
             color = "deepskyblue") +
  geom_line(aes(yearmonth, AfD), color = "deepskyblue") +

  # CDU/CSU
  geom_point(aes(yearmonth, Union), size= 0.5,
             color = "black") +
  geom_line(aes(yearmonth, Union),
             color = "black") +

  # SPD
  geom_point(aes(yearmonth, SPD), size= 0.5,
             color = "red") +
  geom_line(aes(yearmonth, SPD),
             color = "red") +

  # Grüne
  geom_point(aes(yearmonth, Grüne), size= 0.5,
             color = "limegreen") +
  geom_line(aes(yearmonth, Grüne),
             color = "limegreen") +

  # DIE LINKE
  geom_point(aes(yearmonth, Linke), size= 0.5,
             color = "deeppink") +
  geom_line(aes(yearmonth, Linke),
             color = "deeppink") +

  # 
  labs(x="", y="", title=paste(i)) +
    theme(axis.text = element_text(size = 6)) +
  facet_grid(topic_name ~.)

  ggsave(p1, file=paste0("../figs/polls_",i,".png"),
         width = 4, height = 10)

}
```

<!-- <img src="../figs/polls_Bild.de.png", width = "49%"> -->
<!-- <img src="../figs/polls_DIE WELT.png", width = "49%"> -->
<!-- <img src="../figs/polls_FOCUS ONLINE.png", width = "49%"> -->
<!-- <img src="../figs/polls_SPIEGEL ONLINE.png", width = "49%"> -->
<!-- <img src="../figs/polls_stern.de.png", width = "49%"> -->
<!-- <img src="../figs/polls_Tagesschau.de.png", width = "49%"> -->
<!-- <img src="../figs/polls_ZEIT ONLINE.png", width = "49%"> -->
